---
title: "Numbers and Plots for 'SARS-CoV-2 antibody seroprevalence and associated risk factors in an urban district in Cameroon'"
date: "`r Sys.Date()`"
output: word_document
fontsize: 10pt

---
\newpage

```{r readData, echo = FALSE, warning = F, message = F}
source(here::here("scripts/load.R"))
knitr::opts_chunk$set(dev="cairo_pdf")
```

```{r utilityFunctions}
source(here("scripts/utils.R"))
```

# Table 1 Sociodemographic characteristics of the final sample

```{r}
source(here("scripts/sample_characteristics_2.R"))
sample_characteristics_2_table

sample_characteristics_2_table %>% 
  as_tibble() %>% 
  as.data.frame() %>% 
  filter(row_number() != 1) %>% 
  write.xlsx(here("data/source_data_for_figures.xlsx"), 
             sheetName = "Table 1", 
             row.names = FALSE,
             showNA = FALSE,
             append = FALSE)
```


# Figure 1: Crude seroprevalence

```{r fig.width = 7.17, fig.height = 8.22}
source(here("scripts/seropos_euler.R"))

intersecting_inside$original.values %>% 
  as.data.frame() %>% 
  as_tibble(rownames = "category") %>% 
  rename(count = 2) %>% 
  filter(count != 0) %>% 
  mutate(category = str_remove_all(category, "Negative&|Negative")) %>% 
  mutate(category = if_else(category == "", "Negative", category)) %>% 
  as.data.frame() %>% 
  write.xlsx(here("data/source_data_for_figures.xlsx"), 
             sheetName = "Figure 1A", 
             row.names = FALSE,
             showNA = FALSE,
             append = TRUE)




source(here("scripts/pos_age_sex_pyramid.R"))

pos_age_sex %>% 
  as.data.frame() %>% 
   write.xlsx(here("data/source_data_for_figures.xlsx"), 
             sheetName = "Figure 1B", 
             row.names = FALSE,
             showNA = FALSE,
             append = TRUE)


top_plots <- 
  cowplot::plot_grid(plot_grid(seropos_euler_plot, scale = 0.9), 
                   pos_age_sex_pyramid_plot, 
                   nrow = 1, 
                   rel_widths = c(3,7.6), labels = c("A", "B"))

source(here("scripts/map2.R"))

region_prevalence %>% 
  select(-title) %>% 
  rename(prevalence = prev) %>% 
  rename(region = loc_hhld_area) %>% 
  as.data.frame() %>% 
   write.xlsx(here("data/source_data_for_figures.xlsx"), 
             sheetName = "Figure 1C Regions", 
             row.names = FALSE,
             showNA = FALSE,
             append = TRUE)

hhlds_pie %>% 
  select(id = id_hhld, 
         longitude = loc_hhld_long_repel, 
         latitude = loc_hhld_lat_repel, 
         num_individuals = n_hhld_indiv,
         prop_igg_pos_only, 
         prop_igm_pos_only, 
         prop_igg_and_igm_pos = prop_igg_and_igm,
         prop_neg_all = prop_neg
         ) %>% 
   as.data.frame() %>% 
   write.xlsx(here("data/source_data_for_figures.xlsx"), 
             sheetName = "Figure 1C Households", 
             row.names = FALSE,
             showNA = FALSE,
             append = TRUE)
  

cowplot::plot_grid(top_plots, 
                   plot_grid(map2_plot, labels = "C"), 
                   ncol = 1, 
                   rel_heights = c(3,6)
                   )

```


# Table 2: Population-weighted and test-adjusted seroprevalence estimates 

```{r}
source(here("scripts/sero_estim_2.R"))

igg_pos_table_print 

igg_pos_table_print %>% 
  as.data.frame() %>% 
  filter(row_number() != 1) %>% 
  write.xlsx(here("data/source_data_for_figures.xlsx"), 
             sheetName = "Table 2", 
             row.names = FALSE,
             col.names = FALSE,
             showNA = FALSE,
             append = TRUE)
  
```


# Figure 2: Risk factor analysis for SARS-CoV-2 IgG seropositivity

```{r fig.width = 7.5, fig.height = 6.5}
source(here("scripts/infection_regn_2.R"))

infection_regn_plot


all_sections %>% 
  select(labels,
         N = n, 
         number_positive = pos,
         percent_positive = pct,
         univariate_odds_ratio = estimate, 
         univariate_lower_CI = lower_CI, 
         univariate_upper_CI = upper_CI,
         multivariate_odds_ratio = multi_estimate,
         multivariate_lower_CI = multi_lower_CI,
         multivariate_upper_CI = multi_upper_CI) %>% 
  as.data.frame() %>% 
  write.xlsx(here("data/source_data_for_figures.xlsx"), 
             sheetName = "Figure 2", 
             row.names = FALSE,
             showNA = FALSE,
             append = TRUE)
  
  
  
```

# Figure 3: Symptomaticity among IgG seropositive and seronegative respondents

```{r fig.width = 7, fig.height = 8.22}

source(here("scripts/seropos_symptoms_matrix.R"))

df_pos %>% 
  bind_rows(df_neg) %>% 
  select(1:3) %>% 
  as.data.frame() %>% 
  write.xlsx(here("data/source_data_for_figures.xlsx"), 
             sheetName = "Figure 3 A", 
             row.names = FALSE,
             showNA = FALSE,
             append = TRUE)


neg_color <- alpha("dodgerblue2", 0.7) 
pos_color <- alpha("firebrick3", 0.7)
text_color <- "firebrick4"

symptoms_among_igg_positive <- 
  yao %>%
  filter(cat_igg_result == "Positive") %>%
  #filter(mcat_symp != "No symptoms") %>% 
  plot_upset2(mcat_symp,
             sep = "--",
             intersect_max_bars = 10,
             subtitle = "",
             fill = pos_color, 
             theme_axis_text_x_top_size = 7,
             scale_size_continuous_range = c(1.8,2.8),
             denom =  yao %>% filter(cat_igg_result == "Positive"),
             set_size_lab = "Prevalence \n(% and No. with this symptom)",
             intersect_size_lab = "Co-prevalence, \n(% and no. with this combination of symptoms)"
             ) %>% 
  plot_grid() +
  labs(caption = "of 302 IgG seropositive individuals.\n Only the 10 most common symptom combinations are shown") + 
  theme(plot.caption = element_text(size = 6.5, color = "gray10", hjust = 1, family = "Avenir Next"))


yao %>%
  filter(cat_igg_result == "Positive") %>% 
  select(id_of_igg_seropositive_individual = id_ind, 
         symptoms = mcat_symp) %>% 
  as.data.frame() %>% 
  write.xlsx(here("data/source_data_for_figures.xlsx"), 
             sheetName = "Figure 3 B", 
             row.names = FALSE,
             showNA = FALSE,
             append = TRUE)


#source(here("scripts/seropos_symptoms_euler.R"))


source(here("scripts/symptoms_per_sero_cat_plot.R"))

symptoms_per_sero_cat %>% 
  select(igg_result = cat_pos, 
         symptom = mcat_symp,
         n,
         total_at_risk = sum,
         pct_with_symptom = pct) %>% 
  as.data.frame() %>% 
  write.xlsx(here("data/source_data_for_figures.xlsx"), 
             sheetName = "Figure 3 C", 
             row.names = FALSE,
             showNA = FALSE,
             append = TRUE)





plot_grid(
  plot_grid(plot_grid(seropos_symptoms_matrix_plot, scale = 0.77), 
            plot_grid(symptoms_among_igg_positive, scale = 0.98), rel_heights = c(0.4, 0.6), 
            ncol = 1, labels = c("a", "b")),
  plot_grid(symptoms_per_sero_cat_plot, scale = 0.98), 
  ncol = 2, rel_widths = c(5,5.5),
  labels = c("","c"))

```





# Figure 4: Drugs taken by those who were IgG seropositive vs IgG seronegative

```{r fig.width = 7.17, fig.height = 8.22}

pos_igg_only_color <- alpha("firebrick3", 0.6)
neg_color <- alpha("dodgerblue2", 0.7) 


# What medication did you take for your acute symptoms? (Among those who were Igg seropositive)

yao_is_igg_pos <-  
  yao %>% 
  filter(cat_igg_result == "Positive")

yao_is_igg_pos %>% 
  #filter(mcat_consult_any != "No response") %>% 
  mutate(mcat_drug = replace_na(mcat_drug, "None")) %>%
  mutate(mcat_drug = recode(mcat_drug, "No response" = "None")) %>% 
  mutate(mcat_drug = recode(mcat_drug, "No medication" = "None")) %>%
  select(id_of_igg_seropositive_individual = id_ind, 
         medication_taken = mcat_drug
         ) %>% 
  as.data.frame() %>% 
  write.xlsx(here("data/source_data_for_figures.xlsx"), 
             sheetName = "Figure 4A", 
             row.names = FALSE,
             showNA = FALSE,
             append = TRUE)


igg_pos_drugs_plot <- 
  yao_is_igg_pos %>% 
  #filter(mcat_consult_any != "No response") %>% 
  mutate(mcat_drug = replace_na(mcat_drug, "None")) %>% 
  mutate(mcat_drug = recode(mcat_drug, "No response" = "None")) %>% 
  mutate(mcat_drug = recode(mcat_drug, "No medication" = "None")) %>% 
  plot_upset(cat_col = mcat_drug,
             denom = yao_is_igg_pos,
             sep = "--",
             fill = pos_igg_only_color,
             set_size_lab = "Set size, \n % who took this medication", 
             intersect_size_lab = "Intersection size, \n % who took this combination of medications",
             intersect_cutoff = 0, 
             intersect_size_lim_upper = 80, 
             set_size_lim_lower = 100,
             intersect_max_bars = 14,
             intersect_size_scale_x_expand_upper = 0
             ) + 
  labs(caption = "Among 302 IgG seropositive individuals\nOnly the 14 most common combinations are shown.") + 
  theme(plot.caption = element_text(face = "plain"))

yao_is_igg_neg <-  
  yao %>% 
  filter(cat_igg_result == "Negative")

yao_is_igg_neg %>% 
  #filter(mcat_consult_any != "No response") %>% 
  mutate(mcat_drug = replace_na(mcat_drug, "None")) %>%
  mutate(mcat_drug = recode(mcat_drug, "No response" = "None")) %>% 
  mutate(mcat_drug = recode(mcat_drug, "No medication" = "None")) %>%
  select(id_of_igg_seronegative_individual = id_ind, 
         medication_taken = mcat_drug
         ) %>% 
  as.data.frame() %>% 
  write.xlsx(here("data/source_data_for_figures.xlsx"), 
             sheetName = "Figure 4B", 
             row.names = FALSE,
             showNA = FALSE,
             append = TRUE)

igg_neg_drugs_plot <- 
  yao_is_igg_neg %>% 
  #filter(mcat_consult_any != "No response") %>% 
  mutate(mcat_drug = replace_na(mcat_drug, "None")) %>% 
  mutate(mcat_drug = recode(mcat_drug, "No response" = "None")) %>% 
  mutate(mcat_drug = recode(mcat_drug, "No medication" = "None")) %>% 
  plot_upset(cat_col = mcat_drug,
             denom = yao_is_igg_neg,
             sep = "--",
             fill = neg_color,
             set_size_lab = "Set size, \n % who took this medication", 
             intersect_size_lab = "Intersection size, \n % who took this combination of medications",
             intersect_cutoff = 0, 
             intersect_size_lim_upper = 80, 
             set_size_lim_lower = 100,
             intersect_max_bars = 14,
             intersect_size_scale_x_expand_upper = 0
             ) + 
  labs(caption = "Among 669 IgG seronegative individuals\nOnly the 14 most common combinations are shown.") + 
  theme(plot.caption = element_text(face = "plain"))

igg_drugs_plot <- 
  plot_grid(igg_pos_drugs_plot, 
            igg_neg_drugs_plot, ncol = 1, scale = 0.95, 
          labels = "AUTO")

igg_drugs_plot


```


# Supplementary Figure 1

Study flowchart

```{r}

knitr::include_graphics(path = here("plots/study_flowchart.pdf"))

```


# Supplementary Figure 2

Sampling and epicurve 

```{r fig.width=7, fig.height=4}
source(here::here("scripts/epicurve_and_sampling_period.R"))

epicurve_and_sampling %>% 
  as.data.frame() %>% 
  write.xlsx(here("data/source_data_for_figures.xlsx"), 
             sheetName = "Figure S2", 
             row.names = FALSE,
             showNA = FALSE,
             append = TRUE)

epicurve_and_sampling_plot
```


# Supplementary Table 1

Stratum weights
```{r}
options(scipen = 99)
age_sex_weights %>% ## defined in load.R
  mutate(cat_age = factor(cat_age, levels = c("5 - 14", "15 - 29", 
                                              "30 - 44", "45 - 64", "65 +"))) %>% 
  arrange(cat_age) %>% 
  mutate(across(.cols = stratum_size_dhs, 
                .fns = ~ formatC(.x, 2, format = "f"))) %>% 
  select(`Age group` = cat_age, 
         Sex = cat_sex, 
         `DHS stratum size` = stratum_size_dhs, 
         `Sample stratum size` = stratum_size_sample, 
         `Stratum weight` = stratum_weight, 
         `Weight per individual`= weight_per_individual) %>% 
  huxtable()

```


# Supplementary Figure 3

Sampling and seropositivity over time

```{r fig.width=5.5, fig.height=6.88}
source(here("scripts/trend_over_time.R"))

seroprev_over_time %>% 
  as.data.frame() %>% 
  write.xlsx(here("data/source_data_for_figures.xlsx"), 
             sheetName = "Figure S3 A", 
             row.names = FALSE,
             showNA = FALSE,
             append = TRUE)

tests_over_time %>% 
  rename(region = loc_hhld_area) %>% 
  rename(date = dt_quest) %>% 
  pivot_wider(id_cols = date, names_from = region, values_from = tested) %>% 
  mutate(across(.fns = ~ replace_na(.x, 0))) %>% 
  ungroup() %>% 
  as.data.frame() %>% 
  write.xlsx(here("data/source_data_for_figures.xlsx"), 
             sheetName = "Figure S3 B", 
             row.names = FALSE,
             showNA = FALSE,
             append = TRUE)

trend_over_time_plot

```

# Supplementary Figure 4

Seroprevalence confidence interval derivation

A: Estimated densities of bootstrap parameters—prevalence, sensitivity and specificity—from their 95% confidence intervals

B: Histogram of the sensitivity- & specificity-adjusted seroprevalence estimates from 100,000 bootstrapped samples.

```{r fig.width = 7.5, fig.height=5.5}

# source(here::here("scripts/sero_estim_2.R"))

seroprev_conf_int_plot <- ggplot_adjPrevSensSpecCI(
    
  prev =  seroprev_pop_weighted[[1]], ## observed prevalence
  sens = sensit, ## observed sensitivity from validation study
  spec = specif, ## observed specificity from validation study
  prevCI = seroprev_pop_weighted_ci[1:2], ## prevalence 95% confidence interval
  sensCI = sensit_conf_int[1:2], ## sensitivity 95% confidence interval
  specCI = specif_conf_int[1:2], ## specificity 95% confidence interval
  N = 1e5, ## number of bootstrap samples  
  method = "quantile", ## use quantiles to compute seroprev 95% CI
  alpha = 0.05,
  doPlot = FALSE ## no plot
  
)

seroprev_conf_int_plot
```


# Supplementary Figure 5

Range of seropositive percentages per household

```{r fig.width = 7, fig.height=7.91}
## IgG
igg_seropos_pct_distrib_hhld_df  <- 
  yao %>% 
  mutate(cat_igg_num = case_when(cat_igg_result == "Positive" ~ 1, 
                                               TRUE ~ 0
                                               )) %>% 
  group_by(id_hhld) %>% 
  summarise(n = sum(counter), 
            n_positive = sum(cat_igg_num)
            ) %>% 
  mutate(pct_positive = round(100 * n_positive/n))

igg_seropos_pct_distrib_hhld_df %>% 
  as.data.frame() %>% 
  write.xlsx(here("data/source_data_for_figures.xlsx"), 
             sheetName = "Figure S5 A", 
             row.names = FALSE,
             showNA = FALSE,
             append = TRUE)
  

# pull vector for histogram
igg_seropos_pct_distrib_hhld <- 
 igg_seropos_pct_distrib_hhld_df %>% 
  arrange(-pct_positive) %>% 
  pull(pct_positive)


## IgM
igm_seropos_pct_distrib_hhld_df <- 
  yao %>% 
  mutate(cat_igm_num = case_when(cat_igm_result == "Positive" ~ 1, 
                                               TRUE ~ 0
                                               )) %>% 
  group_by(id_hhld) %>% 
  summarise(n = sum(counter), 
            n_positive = sum(cat_igm_num)
            ) %>% 
  mutate(pct_positive = round(100 * n_positive/n))


igm_seropos_pct_distrib_hhld_df %>% 
  as.data.frame() %>% 
  write.xlsx(here("data/source_data_for_figures.xlsx"), 
             sheetName = "Figure S5 B", 
             row.names = FALSE,
             showNA = FALSE,
             append = TRUE)
  

# pull vector for histogram
igm_seropos_pct_distrib_hhld <- 
igm_seropos_pct_distrib_hhld_df %>% 
  arrange(-pct_positive) %>% 
  pull(pct_positive)

## IgG and/or IgM

igg_or_igm_seropos_pct_distrib_hhld_df <- 
  yao %>% 
  mutate(cat_igg_or_igm_result = ifelse(cat_igm_result == "Positive" | cat_igg_result == "Positive", 
                                        "Positive", 
                                        "Negative"
                                        )) %>% 
  mutate(cat_igg_or_igm_result_num = case_when(cat_igg_or_igm_result == "Positive" ~ 1, 
                                               TRUE ~ 0
                                               )) %>% 
  group_by(id_hhld) %>% 
  summarise(n = sum(counter), 
            n_positive = sum(cat_igg_or_igm_result_num)
            ) %>% 
  mutate(pct_positive = round(100 * n_positive/n))


igg_or_igm_seropos_pct_distrib_hhld_df %>% 
  as.data.frame() %>% 
  write.xlsx(here("data/source_data_for_figures.xlsx"), 
             sheetName = "Figure S5 C", 
             row.names = FALSE,
             showNA = FALSE,
             append = TRUE)
  
  
# pull vector for histogram
igg_or_igm_seropos_pct_distrib_hhld <- 
  igg_or_igm_seropos_pct_distrib_hhld_df %>% 
  arrange(-pct_positive) %>% 
  pull(pct_positive)



igg_seropos_distrib_plot <- 
  data.frame(igg_seropos_pct_distrib_hhld, 
           counter = 1) %>% 
  mutate(igg_seropos_pct_distrib_hhld = cut(igg_seropos_pct_distrib_hhld, 
                                        breaks = seq(from = 0, to = 100, by = 10), include.lowest = T)) %>%
  bind_rows(data.frame(igg_seropos_pct_distrib_hhld = cut(1:100, breaks = seq(from = 0, to = 100, by = 10), include.lowest = T),
                       counter = 0)) %>% 
  group_by(igg_seropos_pct_distrib_hhld) %>% 
  summarise(n = sum(counter)) %>% 
  ggplot()+ 
  geom_col(aes(x = igg_seropos_pct_distrib_hhld, y = n), 
           fill = alpha(pos_igg_only_color, 0.7), 
           color = alpha(pos_igg_only_color, 0.9),
           width = 1) + 
  geom_text(aes(x = igg_seropos_pct_distrib_hhld, y = n, label = n),
           color = "black", size = 4, vjust = -0.2) + 
  labs(x = "Household prevalence of IgG antibodies", 
       y = "Count") + 
  scale_y_continuous(limits = c(0, 160))



igm_seropos_distrib_plot <- 
  data.frame(igm_seropos_pct_distrib_hhld, 
           counter = 1) %>% 
  mutate(igm_seropos_pct_distrib_hhld = cut(igm_seropos_pct_distrib_hhld, 
                                        breaks = seq(from = 0, to = 100, by = 10), include.lowest = T)) %>%
  bind_rows(data.frame(igm_seropos_pct_distrib_hhld = cut(1:100, breaks = seq(from = 0, to = 100, by = 10), include.lowest = T),
                       counter = 0)) %>% 
  group_by(igm_seropos_pct_distrib_hhld) %>% 
  summarise(n = sum(counter)) %>% 
  ggplot()+ 
  geom_col(aes(x = igm_seropos_pct_distrib_hhld, y = n), 
           fill = alpha(pos_igm_only_color, 0.7), 
           color = alpha(pos_igm_only_color, 0.9),
           width = 1) + 
  geom_text(aes(x = igm_seropos_pct_distrib_hhld, y = n, label = n),
           color = "black", size = 4, vjust = -0.2) + 
  labs(x = "Household prevalence of IgM antibodies", 
       y = "Count") + 
  scale_y_continuous(limits = c(0, 160))


igm_or_igm_seropos_distrib_plot <- 
  data.frame(igg_or_igm_seropos_pct_distrib_hhld, 
           counter = 1) %>% 
  mutate(igg_or_igm_seropos_pct_distrib_hhld = cut(igg_or_igm_seropos_pct_distrib_hhld, 
                                        breaks = seq(from = 0, to = 100, by = 10), include.lowest = T)) %>%
  bind_rows(data.frame(igg_or_igm_seropos_pct_distrib_hhld = cut(1:100, breaks = seq(from = 0, to = 100, by = 10), include.lowest = T),
                       counter = 0)) %>% 
  group_by(igg_or_igm_seropos_pct_distrib_hhld) %>% 
  summarise(n = sum(counter)) %>% 
  ggplot()+ 
  geom_col(aes(x = igg_or_igm_seropos_pct_distrib_hhld, y = n), 
           fill = alpha(pos_igg_and_igm_color, 0.8), 
           color = alpha(pos_igg_and_igm_color, 0.9),
           width = 1
           ) + 
  geom_text(aes(x = igg_or_igm_seropos_pct_distrib_hhld, y = n, label = n),
           color = "black", size = 4, vjust = -0.2) + 
  labs(x = "Household prevalence of IgM and/or IgM antibodies", 
       y = "Count") + 
  scale_y_continuous(limits = c(0, 160))




cowplot::plot_grid(plot_grid(igg_seropos_distrib_plot, scale = 0.93), 
                   plot_grid(igm_seropos_distrib_plot, scale = 0.93), 
                   plot_grid(igm_or_igm_seropos_distrib_plot, scale = 0.93), 
                   ncol = 1,
                   labels = "AUTO")


print("Median and IQR IgG seropositivity percentages per household:")
print("Median:")
median(igg_seropos_pct_distrib_hhld)
print("IQR:")
quantile(igg_seropos_pct_distrib_hhld, 0.25)
quantile(igg_seropos_pct_distrib_hhld, 0.75)


print("Median and IQR IgM seropositivity percentages per household:")
print("Median:")
median(igm_seropos_pct_distrib_hhld)
print("IQR:")
quantile(igm_seropos_pct_distrib_hhld, 0.25)
quantile(igm_seropos_pct_distrib_hhld, 0.75)


print("Median and IQR IgG or IgM seropositivity percentages per household:")
print("Median:")
median(igg_or_igm_seropos_pct_distrib_hhld)
print("IQR:")
quantile(igg_or_igm_seropos_pct_distrib_hhld, 0.25)
quantile(igg_or_igm_seropos_pct_distrib_hhld, 0.75)
```


# Supplementary Figure 6

Healthcare attention among those who were IgG seropositive vs IgG seronegative

```{r fig.width=7, fig.height=9}

pos_igg_only_color <- alpha("firebrick3", 0.6)
neg_color <- alpha("dodgerblue2", 0.7) 


# Where did you consult for your acute symptoms? (Among those who were Igg seropositive)
yao_is_igg_pos <-  
  yao %>% 
  filter(cat_igg_result == "Positive")

yao_is_igg_pos %>% 
  #filter(mcat_consult_any != "No response") %>% 
  mutate(mcat_consult = replace_na(mcat_consult, "None")) %>%
  mutate(mcat_consult = recode(mcat_consult, "No response" = "None")) %>% 
  select(id_of_igg_seropositive_individual = id_ind, 
         consultations = mcat_consult
         ) %>% 
  as.data.frame() %>% 
  write.xlsx(here("data/source_data_for_figures.xlsx"), 
             sheetName = "Figure S6 A", 
             row.names = FALSE,
             showNA = FALSE,
             append = TRUE)

igg_pos_consult_plot <- 
  yao_is_igg_pos %>% 
  #filter(mcat_consult_any != "No response") %>% 
  mutate(mcat_consult = replace_na(mcat_consult, "None")) %>%
  mutate(mcat_consult = recode(mcat_consult, "No response" = "None")) %>% 
  plot_upset(cat_col = mcat_consult,
             denom = yao_is_igg_pos,
             sep = "--",
             fill = pos_igg_only_color, 
             set_size_lab = "Set size, \n % who consulted here", 
             intersect_size_lab = "Intersection size, \n % who consulted with this combination",
             intersect_cutoff = 0, 
             intersect_size_scale_x_expand_upper = 0, 
             set_size_lim_lower = 100,
             intersect_size_lim_upper = 98 ) + 
  labs(caption = "Among 302 IgG seropositive individuals") + 
  theme(plot.caption = element_text(face = "plain"))





yao_is_igg_neg <-  
  yao %>% 
  filter(cat_igg_result == "Negative")

yao_is_igg_neg %>% 
  #filter(mcat_consult_any != "No response") %>% 
  mutate(mcat_consult = replace_na(mcat_consult, "None")) %>%
  mutate(mcat_consult = recode(mcat_consult, "No response" = "None")) %>% 
  select(id_of_igg_seronegative_individual = id_ind, 
         consultations = mcat_consult
         ) %>% 
  as.data.frame() %>% 
  write.xlsx(here("data/source_data_for_figures.xlsx"), 
             sheetName = "Figure S6 B", 
             row.names = FALSE,
             showNA = FALSE,
             append = TRUE)

igg_neg_consult_plot <- 
  yao_is_igg_neg %>% 
  #filter(mcat_consult_any != "No response") %>% 
  mutate(mcat_consult = replace_na(mcat_consult, "None")) %>% 
  mutate(mcat_consult = recode(mcat_consult, "No response" = "None")) %>% 
  plot_upset(cat_col = mcat_consult,
             denom = yao_is_igg_neg,
             sep = "--",
             fill = neg_color,
             set_size_lab = "Set size, \n % who consulted here", 
             intersect_size_lab = "Intersection size, \n % who consulted with this combination",
             intersect_cutoff = 0, 
             intersect_size_lim_upper = 98,
             set_size_lim_lower = 100,
             intersect_size_scale_x_expand_upper = 0) + 
  labs(caption = "Among 669 IgG seronegative individuals") + 
  theme(plot.caption = element_text(face = "plain"))


igg_consult_plot <- 
  plot_grid(igg_pos_consult_plot, 
            igg_neg_consult_plot, ncol = 1, scale = 0.95, 
          labels = "AUTO")

igg_consult_plot

```

# Other Key numbers for paper


## Number of IgG positives who did not consult any care

```{r}

consult_and_non_consult <- 
  yao %>% 
  filter(cat_igg_result == "Positive") %>% 
  mutate(mcat_consult = replace_na(mcat_consult, "None")) %>% 
  mutate(consulted_care = ifelse(mcat_consult == "None", "No consultation", "Consulted care")) %>% 
  tabyl(consulted_care)


consult_and_non_consult

BinomCI(x = consult_and_non_consult$n[2], 
        n = sum(consult_and_non_consult$n)) %>% 
  as.data.frame() %>% 
  huxtable(add_colnames = TRUE)

```

## Among those who were IgG seropositive, what percentage reported any symptoms?

```{r}
with_and_without_symp <- 
  yao %>% 
  filter(cat_igg_result == "Positive") %>% 
  tabyl(has_acute_symp)


with_and_without_symp
BinomCI(x = with_and_without_symp$n[1], 
        n = sum(with_and_without_symp$n)) %>% 
    as.data.frame() %>% 
  huxtable(add_colnames = TRUE)

```


## What percentage (of household representatives) reported reduced income?

```{r}

rev_dropped_tabyl <- 
  yao_hhld_heads %>% 
  tabyl(has_rev_dropped)

rev_dropped_tabyl

BinomCI(x = rev_dropped_tabyl$n[3],
        n = sum(rev_dropped_tabyl$n)
  
)


```


## Number of seropositive participants per household

```{r}

seropos_per_hhld <- 
  yao %>% 
  mutate(cat_igg_or_igm_result = ifelse(cat_igm_result == "Positive" | cat_igg_result == "Positive", 
                                        "Positive", 
                                        "Negative"
                                        )) %>% 
  mutate(cat_igg_or_igm_result_num = case_when(cat_igg_or_igm_result == "Positive" ~ 1, 
                                               TRUE ~ 0
                                               )) %>% 
  group_by(id_hhld) %>% 
  summarise(n = sum(counter), 
            n_positive = sum(cat_igg_or_igm_result_num)) %>% 
  mutate(pct_positive = round(100 * n_positive/n)) %>% 
  count(n_positive) %>% 
  mutate(pct = percent(n/ sum(n), accuracy = 0.1))

print("Percentage of households with at least one seropositive participant:")
numerator <- seropos_per_hhld %>% filter(n_positive > 0) %>% pull(n) %>% sum()
denominator <- seropos_per_hhld %>% pull(n) %>% sum()

percent(numerator/denominator)
print(paste("(", numerator, "out of", denominator, ")"))
  
```


## Mean household members per neighbourhood

```{r}
yao %>% 
  group_by(loc_hhld_area) %>% 
  summarise(mean_residents = mean(n_hhld_indiv), 
            sd_residents = sd(n_hhld_indiv)) %>% 
  arrange(2) %>% 
  huxtable()

```


## Other numbers requested

```{r}
# begin date for survey
min_dt_quest <- 
  yao$dt_quest %>% 
  min(na.rm = T) %>% 
  format.Date(format = "%d %B")

# end date for survey
max_dt_quest <- 
  yao$dt_quest %>% 
  max(na.rm = T) %>% 
  format.Date(format = "%d %B, %Y")
  
# n of households
n_hhlds_included <- 
  yao$id_hhld %>% 
    unique() %>% 
    length()

# n of individuals    
n_ind_included <- 
  yao$id_ind %>% 
    unique() %>% 
    length()

# mean adults per hhld
mean_n_adults_per_hhld <- 
  yao_hhld$n_hhld_adults %>% 
  mean() %>% 
  round(1)
  
# mean children per hhld
mean_n_children_per_hhld <- 
  yao_hhld$n_hhld_children %>% 
  mean() %>% 
  round(1)

# number of households without a head
n_hhlds_w_o_head <- 
  yao %>% 
  group_by(id_hhld) %>% 
  transmute(is_head = ifelse(is_head == "Yes", 1, 0)) %>% 
  mutate(head_sum = sum(is_head)) %>% 
  slice(1) %>% 
  ungroup() %>% 
  filter(head_sum == 0) %>% 
  nrow()

# percentage of households without a head
pct_hhlds_w_o_head <- 
  (100 * n_hhlds_w_o_head/n_hhlds_included) %>% 
  round(1)

  
# number of households where we could access breadwinner
n_hhlds_w_breadwin <- 
  yao %>% 
  group_by(id_hhld) %>% 
  transmute(is_breadwin = ifelse(is_breadwin == "Yes", 1, 0)) %>% 
  mutate(is_breadwin = sum(is_breadwin)) %>% 
  slice(1) %>% 
  ungroup() %>% 
  filter(is_breadwin > 0) %>% 
  nrow()

# percentage of households where we could access breadwinner
pct_hhlds_w_breadwin <- 
  (100 * n_hhlds_w_breadwin/n_hhlds_included) %>% 
  round(1)

# percentage of hhlds in which the father is breadwinner
pct_hhlds_w_father_breadwin <- 
  (((yao_hhld %>% 
  filter(is_breadwin_father == 1) %>% 
  nrow())/n_hhlds_included)* 100) %>% 
  round(1)
  
# percentage of hhlds in which the mother is breadwinner
pct_hhlds_w_mother_breadwin <- 
  (((yao_hhld %>% 
  filter(is_breadwin_mother == 1) %>% 
  nrow())/n_hhlds_included)* 100) %>% 
  round(1)

# top 4 occupations
top_four_occupations <- 
  yao %>% 
  select(mcat_occup) %>% 
  separate_rows(sep = "--") %>% 
  count(mcat_occup) %>% 
  arrange(-n) %>% 
  head(4) %>% 
  pull(mcat_occup) %>% 
  paste(., collapse = ", ")
 

# pct with death during pandemic
pct_with_death <- 
  (yao_hhld %>% 
  filter(has_hhld_death == "Yes") %>% 
  nrow()*100/n_hhlds_included) %>% 
  round(1)
  
# mean age of death during pandemic
mean_age_death <- 
  yao_hhld %>%  
  filter(!is.na(val_dead1_age)) %>% 
  .$val_dead1_age %>% 
  mean()

# number with positive test
n_hhlds_with_pos_test <- 
  yao_hhld %>%
  filter(has_mem_tested_positive == "Yes") %>% 
  nrow()

# Number with any COVID-like symptoms
n_inds_with_symptoms <- 
  yao %>% 
  filter(mcat_symp != "No symptoms") %>% 
  nrow()

# Percentage with any COVID-like symptoms
pct_inds_with_symptoms <- 
  ((100 * n_inds_with_symptoms)/nrow(yao)) %>% 
  round(1)
  
# Number seropositive
n_seropositive <- 
  yao %>% 
  filter(cat_igg_result == "Positive" | cat_igm_result == "Positive" ) %>% 
  nrow()

# Number seropositive
n_seronegative <- 
  yao %>% 
  filter(cat_igg_result == "Negative" & cat_igm_result == "Negative" ) %>% 
  nrow()

n_igg_seropos_symptoms_mild_or_moderate <- 
  yao %>% 
  filter(cat_igg_result == "Positive") %>% 
  filter(cat_symp_severity == "Mild" | cat_symp_severity == "Moderate") %>% 
  nrow()

n_igg_seropos_w_symptoms <- 
  yao %>% 
  filter(cat_igg_result == "Positive") %>% 
  filter(cat_symp_severity == "Mild" | cat_symp_severity == "Moderate" 
          | cat_symp_severity == "Severe") %>% 
  nrow()

source(here::here("scripts/test_performance.R"))
igg_test_performance_table <- igg_test_performance_table ## just so you remember where these came from
igm_test_performance_table <- igm_test_performance_table


```

-   IgG Test sensitivity and specificity: `r igg_test_performance_table`

-   IgM Test specificity: `r igm_test_performance_table`

-   Date of first survey: `r min_dt_quest`

-   Date of last survey: `r max_dt_quest`

-   Number of households surveyed: `r n_hhlds_included`

-   Number of individuals surveyed: `r n_ind_included`

-   Mean number of adults per household: `r mean_n_adults_per_hhld`

-   Mean number of children per household: `r mean_n_children_per_hhld`

-   Number of household where the head was not interviewed: `r n_hhlds_w_o_head`

-   Percentage of household where the head was not interviewed: `r pct_hhlds_w_o_head`%

-   Number of households where the breadwinner was interviewed: `r n_hhlds_w_breadwin`

-   Percentage of households where the breadwinner was interviewed: `r pct_hhlds_w_breadwin`%

-   Percentage of households in which the father is the breadwinner: `r pct_hhlds_w_father_breadwin`%

-   Percentage of households in which the mother is the breadwinner: `r pct_hhlds_w_mother_breadwin`%

-   Top four occupations: `r top_four_occupations`

-   Percentage of households where there has been a death since March 1st: `r pct_with_death`

-   Mean age of those who diead since March 1st: `r mean_age_death`

-   Number of households where a prior positive test was reported: `r n_hhlds_with_pos_test`

-   Number of individuals who have reported any COVID-like symptoms: `r n_inds_with_symptoms`

-   Percentage of individuals who have reported any COVID-like symptoms: `r pct_inds_with_symptoms`

-   Number seropositive (either IgG or IgM): `r n_seropositive`

-   Number seronegative (both IgG and IgM): `r n_seronegative`

-   Number of IgG seropositive with symptoms: `r n_igg_seropos_w_symptoms`

-   Number of IgG seropositive with symptoms described as mild or moderate: `r n_igg_seropos_symptoms_mild_or_moderate`





