---
title: "Numbers and figures requested for Prelim report"
date: "`r Sys.Date()`"

## Options for outputting HTML

# output:
#   rmarkdown::html_document:
#     theme: cerulean
#     toc: true
#     toc_depth: 2
#     toc_float: true
# 


# Options for outputting PDF
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: true
    number_sections: true
    latex_engine: xelatex
    includes:
      in_header: preamble.tex
mainfont: Avenir
fontsize: 10pt
geometry: left=2cm,right=2cm,top=2.5cm,bottom=2cm


## Options for outputting Word
# output: word_document
# fontsize: 10pt


## Other options
# editor_options: 
#   chunk_output_type: console
# params: 
#   mode: "word"
---

\newpage

```{r readData}
library(here)
source(here("scripts/load.R"))
```

```{r utilityFunctions}
source(here("scripts/utils.R"))
```

# Specific numbers requested

```{r}
# begin date for survey
min_dt_quest <- 
  yao$dt_quest %>% 
  min(na.rm = T) %>% 
  format.Date(format = "%d %B")

# end date for survey
max_dt_quest <- 
  yao$dt_quest %>% 
  max(na.rm = T) %>% 
  format.Date(format = "%d %B, %Y")
  
# n of households
n_hhlds_included <- 
  yao$id_hhld %>% 
    unique() %>% 
    length()

# n of individuals    
n_ind_included <- 
  yao$id_ind %>% 
    unique() %>% 
    length()

# mean adults per hhld
mean_n_adults_per_hhld <- 
  yao_hhld$n_hhld_adults %>% 
  mean() %>% 
  round(1)
  
# mean children per hhld
mean_n_children_per_hhld <- 
  yao_hhld$n_hhld_children %>% 
  mean() %>% 
  round(1)

# number of households without a head
n_hhlds_w_o_head <- 
  yao %>% 
  group_by(id_hhld) %>% 
  transmute(is_head = ifelse(is_head == "Yes", 1, 0)) %>% 
  mutate(head_sum = sum(is_head)) %>% 
  slice(1) %>% 
  ungroup() %>% 
  filter(head_sum == 0) %>% 
  nrow()

# percentage of households without a head
pct_hhlds_w_o_head <- 
  (100 * n_hhlds_w_o_head/n_hhlds_included) %>% 
  round(1)

  
# number of households where we could access breadwinner
n_hhlds_w_breadwin <- 
  yao %>% 
  group_by(id_hhld) %>% 
  transmute(is_breadwin = ifelse(is_breadwin == "Yes", 1, 0)) %>% 
  mutate(is_breadwin = sum(is_breadwin)) %>% 
  slice(1) %>% 
  ungroup() %>% 
  filter(is_breadwin > 0) %>% 
  nrow()

# percentage of households where we could access breadwinner
pct_hhlds_w_breadwin <- 
  (100 * n_hhlds_w_breadwin/n_hhlds_included) %>% 
  round(1)

# percentage of hhlds in which the father is breadwinner
pct_hhlds_w_father_breadwin <- 
  (((yao_hhld %>% 
  filter(is_breadwin_father == 1) %>% 
  nrow())/n_hhlds_included)* 100) %>% 
  round(1)
  
# percentage of hhlds in which the mother is breadwinner
pct_hhlds_w_mother_breadwin <- 
  (((yao_hhld %>% 
  filter(is_breadwin_mother == 1) %>% 
  nrow())/n_hhlds_included)* 100) %>% 
  round(1)

# top 4 occupations
top_four_occupations <- 
  yao %>% 
  select(mcat_occup) %>% 
  separate_rows(sep = "--") %>% 
  count(mcat_occup) %>% 
  arrange(-n) %>% 
  head(4) %>% 
  pull(mcat_occup) %>% 
  paste(., collapse = ", ")
 

# pct with death during pandemic
pct_with_death <- 
  (yao_hhld %>% 
  filter(has_hhld_death == "Yes") %>% 
  nrow()*100/n_hhlds_included) %>% 
  round(1)
  
# mean age of death during pandemic
mean_age_death <- 
  yao_hhld %>%  
  filter(!is.na(val_dead1_age)) %>% 
  .$val_dead1_age %>% 
  mean()

# number with positive test
n_hhlds_with_pos_test <- 
  yao_hhld %>%
  filter(has_mem_tested_positive == "Yes") %>% 
  nrow()

# Number with any COVID-like symptoms
n_inds_with_symptoms <- 
  yao %>% 
  filter(mcat_symp != "No symptoms") %>% 
  nrow()

# Percentage with any COVID-like symptoms
pct_inds_with_symptoms <- 
  ((100 * n_inds_with_symptoms)/nrow(yao)) %>% 
  round(1)
  
# percentage complete or partial compliance with preventive measures
pct_respecting_distancing <- 
  ((yao %>% 
  filter(is_respecting_distancing == "Definitely Yes" | is_respecting_distancing == "Partly"  ) %>% 
  nrow() * 100)/nrow(yao)) %>% 
  round(1)

# Number seropositive
n_seropositive <- 
  yao %>% 
  filter(cat_igg_result == "Positive" | cat_igm_result == "Positive" ) %>% 
  nrow()

# Number seropositive
n_seronegative <- 
  yao %>% 
  filter(cat_igg_result == "Negative" & cat_igm_result == "Negative" ) %>% 
  nrow()

```

-   Date of first survey: `r min_dt_quest`

-   Date of last survey: `r max_dt_quest`

-   Number of households surveyed: `r n_hhlds_included`

-   Number of individuals surveyed: `r n_ind_included`

-   Mean number of adults per household: `r mean_n_adults_per_hhld`

-   Mean number of children per household: `r mean_n_children_per_hhld`

-   Number of household where the head was not interviewed: `r n_hhlds_w_o_head`

-   Percentage of household where the head was not interviewed: `r pct_hhlds_w_o_head`%

-   Number of households where the breadwinner was interviewed: `r n_hhlds_w_breadwin`

-   Percentage of households where the breadwinner was interviewed: `r pct_hhlds_w_breadwin`%

-   Percentage of households in which the father is the breadwinner: `r pct_hhlds_w_father_breadwin`%

-   Percentage of households in which the mother is the breadwinner: `r pct_hhlds_w_mother_breadwin`%

-   Top four occupations: `r top_four_occupations`

-   Percentage of households where there has been a death since March 1st: `r pct_with_death`

-   Mean age of those who diead since March 1st: `r mean_age_death`

-   Number of households where a prior positive test was reported: `r n_hhlds_with_pos_test`

-   Number of individuals who have reported any COVID-like symptoms: `r n_inds_with_symptoms`

-   Percentage of individuals who have reported any COVID-like symptoms: `r pct_inds_with_symptoms`

-   Percentage of individuals who are completely or partially complying with social distancing: `r pct_respecting_distancing`%

-   Number seropositive (either IgG or IgM): `r n_seropositive`

-   Number seronegative (both IgG and IgM): `r n_seronegative`



\newpage

# Respondent characteristics

## Sociodemographic characteristics of the final sample

Below is the sample table. Still needs lots of work: More variables, percentages. A similar table that is faceted by seropositivity instead of sex may also be good.

```{r}

sex_count <- 
  yao %>% 
  # summarise
  group_by(cat_sex) %>% 
  count(id_ind) %>% 
  count(n) %>% 
  ungroup() %>% 
  mutate(pct = 100*nn/sum(nn),
         pct = round(pct, 1),
         nn_pct = paste0(nn, " (", pct, "%)")) %>% 
  # add total
  add_row(cat_sex = "Total", 
          nn = sum(.$nn),
          nn_pct = as.character(sum(.$nn)) ) %>% 
  # transform
  select(Sex = cat_sex,
         #nn_pct ,
         nn) %>% 
  mutate(Characteristic = "n") %>% 
  pivot_wider(id_cols = Characteristic, values_from = nn, names_from = Sex) %>% 
  mutate(across(.fns = as.character))


  
hhld_head_m_f <- 
  yao %>% 
  # summarise
  group_by(cat_sex) %>% 
  summarise(n = sum(is_head == "Yes")) %>% 
  ungroup() %>% 
  # add total 
  add_row(cat_sex = "Total",
          n = sum(.$n)) %>% 
  # transform
  #mutate(Characteristic = "Household heads, n (%)") %>% 
  mutate(Characteristic = "Num. household heads") %>% 
  rename(Sex = cat_sex) %>% 
  pivot_wider(id_cols = Characteristic, values_from = n, names_from = Sex) %>% 
  mutate(across(.fns = as.character))
  

mean_age <- 
  yao %>% 
  # summarise
  group_by(cat_sex) %>% 
  summarise(mean_age = format(mean(val_age), digits = 3 ) , 
            sd = format(sd(val_age), digits = 3), 
            mean_sd = paste0(mean_age, " (", sd, ")")
            ) %>% 
  ungroup() %>% 
  # add total
  add_row(cat_sex = "Total",
          mean_age = format(mean(yao$val_age), digits = 3 ), 
          sd = format(sd(yao$val_age), digits = 3)) %>% 
  mutate(mean_sd = ifelse(cat_sex == "Total", 
                          paste0(mean_age, " (", sd, ")"),
                          mean_sd)) %>% 
  # transform
  mutate(Characteristic = "Mean Age (SD)") %>% 
  pivot_wider(id_cols = Characteristic, values_from = mean_sd, names_from = cat_sex)


BMI_row <- 
  yao %>% 
  # summarise
  group_by(cat_sex) %>% 
  summarise(mean_BMI = format(mean(val_BMI), digits = 3 ) , 
            sd = format(sd(val_BMI), digits = 3), 
            mean_sd = paste0(mean_BMI, " (", sd, ")")
            ) %>% 
  ungroup() %>% 
  # add total
  add_row(cat_sex = "Total",
          mean_BMI = format(mean(yao$val_BMI), digits = 3 ), 
          sd = format(sd(yao$val_BMI), digits = 3)) %>% 
  mutate(mean_sd = ifelse(cat_sex == "Total", 
                          paste0(mean_BMI, " (", sd, ")"),
                          mean_sd)) %>% 
  # transform
  mutate(Characteristic = "Mean BMI (SD)") %>% 
  pivot_wider(id_cols = Characteristic, values_from = mean_sd, names_from = cat_sex)


tabulate_categories <- function(df, col) {
  df %>%
    # count
    group_by(cat_sex, {{ col }}) %>%
    count(id_ind) %>%
    count(n) %>%
    ungroup() %>%
    # add percentages
    group_by(cat_sex) %>%
    mutate(
      pct = 100 * nn / sum(nn),
      pct = round(pct, 1)
    ) %>%
    ungroup() %>%
    # add total
    add_row(cat_sex = "Total") %>%
    complete(cat_sex, {{ col }}) %>%
    group_by({{ col }}) %>%
    mutate(nn = ifelse(cat_sex == "Total",
                       sum(nn, na.rm = T), nn)) %>%
    group_by(cat_sex) %>%
    mutate(pct = ifelse(cat_sex == "Total",
                        round(100 * nn / sum(nn, na.rm = T), 1),
                        pct)) %>%
    filter(!is.na({{ col }})) %>%
    {
      suppressWarnings(mutate(., across(.fns = ~ replace_na(.x, 0))))
    } %>%
    # paste count and percentages
    mutate(nn = format(nn, digits = 3)) %>%
    mutate(nn_pct = paste0(nn, " (", pct, "%)")) %>%
    # transform
    select(Characteristic = {{ col }},
           Sex = cat_sex,
           nn_pct) %>%
    pivot_wider(id_cols = Characteristic, values_from = nn_pct, names_from = Sex) %>%
    mutate(across(.fns = as.character))
}


age_groups <- 
  yao %>% 
  # count
  tabulate_categories(cat_age)


education_levels <- 
  yao %>% 
  mutate(cat_educ = recode(cat_educ, "No response" = "Other")) %>% 
  mutate(cat_educ = fct_infreq(cat_educ), 
         cat_educ = fct_relevel(cat_educ, "Other", after = Inf)) %>% 
  tabulate_categories(cat_educ)


professions <- 
  yao %>% 
  # separate
  select(cat_sex, id_ind, mcat_occup) %>% 
  separate_rows(mcat_occup, sep = "--") %>% 
  mutate(mcat_occup = recode(mcat_occup, "No response" = "Other")) %>% 
  mutate(mcat_occup = fct_infreq(mcat_occup)) %>% 
  tabulate_categories(mcat_occup)


chronic_illnesses <- 
  yao %>% 
  # separate
  select(cat_sex, id_ind, mcat_chronic) %>% 
  separate_rows(mcat_chronic, sep = "--") %>% 
  mutate(mcat_chronic = recode(mcat_chronic, "Other chronic illness" = "Other")) %>% 
  mutate(mcat_chronic = fct_infreq(mcat_chronic), 
          mcat_chronic = fct_relevel(mcat_chronic, "Other", after = Inf)) %>% 
  # count
  tabulate_categories(mcat_chronic)


sample_table <- 
  sex_count %>% 
  bind_rows(hhld_head_m_f) %>% 
  bind_rows(mean_age) %>% 
  bind_rows(BMI_row) %>% 
  add_row(Characteristic  = "Age groups, n (% of sex in each group)") %>% 
  bind_rows(age_groups) %>% 
  add_row(Characteristic  = "Education Level, n (% of sex in each group)") %>% 
  bind_rows(education_levels) %>% 
  add_row(Characteristic  = "Profession, n (% of sex in each group)") %>% 
  bind_rows(professions) %>% 
  add_row(Characteristic  = "Chronic conditions, n (% of sex with that condition)") %>% 
  bind_rows(chronic_illnesses) %T>% 
  {which(is.na(.$Female)) ->> rows_to_merge } %>% 
  huxtable() %>% 
  theme_basic() %>% 
  merge_across(row = rows_to_merge + 1) %>% 
  set_italic(row = c(rows_to_merge + 1), col = 1) %>% 
  set_latex_float("h!") %>% 
  set_all_padding(0.5)

sample_table

```

\newpage


# Seroprevalence estimates

## Seropositivity of respondents by test type


```{r fig.width = 2, fig.height = 1.5}


intersecting_inside <- euler(c("Negative" = yao %>% filter(cat_igg_result == "Negative" & cat_igm_result == "Negative") %>% nrow(), 
                               "IgG Positive" = 0, #B
                               "IgM Positive" = 0,  #c
                               "Negative&IgG Positive" = yao %>% filter(cat_igg_result == "Positive") %>% nrow(), 
                               "Negative&IgM Positive"  = yao %>% filter(cat_igm_result == "Positive") %>% nrow(), 
                               "IgG Positive&IgM Positive" = 0,  # Not part of the all_respondents set
                               "Negative&IgG Positive&IgM Positive" = yao %>% filter(cat_igg_result == "Positive" & cat_igm_result == "Positive") %>% nrow()))



plot(intersecting_inside,
     fills = list(fill = c("gray90",
                           "lightblue2",
                           "lightgoldenrod2",
                           "",
                           "",
                           "",
                           "mediumaquamarine")),
     legend = list(side = "right", 
                   fontfamily = "Avenir"), 
     quantities = list(type = "counts",
                       font = 3, 
                       fontfamily = "Avenir"), 
     edges = list(col = "transparent"))


```

## Seropositivity in each age-sex stratum. 

Positive cases include individuals positive for either IgG or IgM antibodies. Inconclusive results are not included in the denominator for the percentages.

```{r fig.width = 6, fig.height = 4}

# yao %>% 
#   filter(val_age > 69) %>% 
#   filter(cat_sex == "femme") %>% 
#   filter(cat_igg_result == "Positive" | cat_igm_result == "Positive") %>% 
#   nrow()

pos_age_sex <- 
  yao %>% 
  # create a counter column
  mutate(pos_test = if_else(cat_igg_result == "Positive" | cat_igm_result == "Positive", 1, 0)) %>% 
  mutate(neg_test = if_else(cat_igg_result == "Negative" & cat_igm_result == "Negative", 1, 0)) %>% 
  group_by(cat_age, cat_sex) %>% 
  summarise(neg_test = sum(neg_test, na.rm = T), 
            pos_test = sum(pos_test, na.rm = T)) %>% 
  mutate(total_count = neg_test + pos_test) %>% 
  ungroup() %>% 
  mutate(cat_sex = recode(cat_sex, "femme" = "Female", "homme" = "Male"))
  


pos_age_sex_long <- 
  pos_age_sex %>% 
  select(-total_count) %>% 
  pivot_longer(names_to = "classification", cols = c(neg_test, pos_test)) %>% 
  mutate(classification  = fct_rev(classification))
  
pos_color <- "#eb9f52"
neg_color <- alpha(my_green,  0.8)

pos_age_sex_long %>%
  ggplot() +
  # males
  geom_bar(data=subset(pos_age_sex_long, cat_sex=="Male"),
                 aes(y=cat_age,x=value,fill=classification),
                 stat="identity",position = "stack", color="white", width = 1,size = 0.1) +
  # add a scale. We don't want a legend for cases. Only deaths, so we pass only a single value to the breaks argument
  scale_fill_manual( breaks = c("Positive"), values = c(pos_color, neg_color )) +
  # ggnewscale allows us to fill males and females with a slightly different color for cases
  ggnewscale::new_scale_fill() +
  # females
  geom_bar(data=subset(pos_age_sex_long, cat_sex=="Female"),
           # negative values for the women
           aes(y=cat_age, x=-value,fill=classification), 
           stat="identity",position = "stack", color="white", width = 1,size = 0.1) +
  # add a scale. We don't want a legend for cases. Only deaths, so we pass only a single value to the breaks argument
  scale_fill_manual( breaks = c("Positive"), values = c(pos_color, neg_color)) +
  # Pos rate labels for males and females (bold font)
  geom_label(data=subset(pos_age_sex,cat_sex=="Male"),
             aes(y=cat_age, x=total_count, label = paste0("Pos: ", round(100* pos_test/total_count, 1), "%")),
             size = 2.7,  fontface = "bold", 
             hjust = 0, vjust = 0.2, label.size = 0, fill = "transparent") +
  geom_label(data=subset(pos_age_sex,cat_sex=="Female"),
             aes(y=cat_age, x=-total_count, label = paste0("Pos: ", round(100* pos_test/total_count, 1), "%")),
             size = 2.7,  fontface = "bold", 
             hjust = 1, vjust = 0.2, label.size = 0, fill = "transparent") +
  # Pos and total count labels (plain font)
  geom_label(data=subset(pos_age_sex,cat_sex=="Male"),
             aes(y=cat_age, x=total_count, label = paste0("(",pos_test, " of ", total_count, ")")),
             size = 2.5,  fontface = "plain", 
             hjust = 0, vjust = 1, label.size = 0, fill = "transparent") +
  geom_label(data=subset(pos_age_sex,cat_sex=="Female"),
             aes(y=cat_age, x=-total_count, label = paste0("(",pos_test, " of ", total_count, ")")),
             size = 2.5,  fontface = "plain", 
             hjust = 1, vjust = 1, label.size = 0, fill = "transparent") +
  # Female and male labels
  # We put in manual annotations for where to place the FEMALE and MALE headers.
  # these are anchored to the mean value of case counts * 2.2
  annotate("label", y= 6, x = -mean(pos_age_sex$total_count)* 1.2, label = "Female", size = 4, fontface = "bold", colour = "white", fill =  "black") +
  annotate("label", y= 6, x = mean(pos_age_sex$total_count)* 1.2, label = "Male", size = 4 , fontface = "bold", colour = "white", fill = "black" ) +
  labs(x = "Count of seropositive and seronegative individuals", y = "") +
  theme(legend.title = element_blank(),
        legend.position = "bottom", 
        axis.text.y = element_text(face = "bold", size = 10, color = "black")) +
  # expand the scale so that text labels are not cut off
  scale_x_continuous(limits = range(c(pos_age_sex$total_count * 1.25, -pos_age_sex$total_count* 1.25 ),na.rm=T) ,
                     labels = abs) +
  scale_y_discrete(expand = expansion(add = c(0,1.4)))
```


## Population-weighted and test-adjusted seroprevalence estimates 

```{r}
source(here("scripts/sero_estim.R"))

igg_pos_table_print

igm_pos_table_print
```


# COVID-19 related Symptoms


## Symptoms among all symptomatic individuals

```{r fig.width=7, fig.height= 3.6}

yao %>%
  filter(mcat_symp != "No symptoms") %>%
  plot_upset(mcat_symp,
             intersect_cutoff = 3,
             denom = yao,
             sep = "--",
             set_size_lab = "Prevalence \n(n and % with this symptom)",
             intersect_size_lab = "Co-prevalence \n (n and % with this combination of symptoms)"
             )


```





## Common symptoms in seropositive and seronegative individuals

```{r fig.width=3.5, fig.height=5}

sero_symptom_chi_square <- function(df, symp_name){

p_val <- (df %>% 
  filter(mcat_symp == symp_name) %>% 
  # count those without the symp. There's prob a cleaner way
  add_row(cat_pos = "Positive", 
          mcat_symp = paste0("No", symp_name), 
          n = .$sum[which(.$cat_pos == "Positive")] - 
            .$n[which(.$cat_pos == "Positive")] ) %>% 
    add_row(cat_pos = "Negative", 
          mcat_symp = paste0("No", symp_name), 
          n = .$sum[which(.$cat_pos == "Negative")] - 
            .$n[which(.$cat_pos == "Negative")] ) %>% 
  # pivot into contigency table
  select(-c(sum, pct)) %>% 
  pivot_wider(id_cols = cat_pos, names_from = mcat_symp, values_from = n) %>% 
  column_to_rownames(var="cat_pos") %>% 
  # run chi square
  chisq.test())$p.value

out <- paste(symp_name, p_val, sep = "--")

return(out)

}


count_pos <- 
  yao %>% 
  count(cat_pos) %>% 
  rename(sum = n)

pos_cnt_for_caption <- count_pos[1,2]
neg_cnt_for_caption <- count_pos[2,2]
seropos_color <- my_orange
seroneg_color <-  my_green



symptoms_per_sero_cat <- 
  yao %>% 
  separate_rows(mcat_symp, sep = "--") %>% 
  group_by(cat_pos, mcat_symp) %>% 
  count() %>%
  ungroup() %>% 
  left_join(count_pos) %>% 
  mutate(pct = 100*n/sum) %>% 
  filter(!is.na(cat_pos)) %>% 
  filter(mcat_symp != "No symptoms") 


symptoms_chi <- map(.x = unique(symptoms_per_sero_cat$mcat_symp), 
    .f = ~ sero_symptom_chi_square(df = symptoms_per_sero_cat, symp_name = .x) ) %>% 
  flatten_chr() %>% 
  as_tibble() %>% 
  separate(col = value, into = c("mcat_symp", "p_val"), sep = "--", remove = TRUE) %>% 
  mutate(p_val = as.numeric(p_val))


symptoms_per_sero_cat %>%
  left_join(symptoms_chi) %>%
  mutate(mcat_symp = fct_reorder(mcat_symp, n)) %>%
  mutate(cat_pos = fct_rev(cat_pos)) %>%
  mutate(cat_pos = recode(cat_pos,
    "Negative" = "Seronegative",
    "Positive" = "Seropositive")) %>%
  mutate(p_val = round(p_val, digits = 2),
         p_val_paste = paste0("p = ", p_val), 
         pct = round(pct, 1),
         hjust = ifelse(pct < 2, 0, 1), 
         color = ifelse(hjust == 0, "black", "white"))%>%
  {
    ggplot(.) +
      geom_col(aes(x = pct, y = mcat_symp, fill = cat_pos),
               position = position_dodge(width = 0.8), width = 0.8) +
      geom_richtext(data = filter(., cat_pos == "Seropositive"), 
                    aes(x = pct, y = mcat_symp, fill = cat_pos, 
                        label = pct, hjust = hjust, color = color), 
                    position = position_nudge(y = +0.2), 
                    size = 2.6, fill = "transparent",
                    label.padding = unit(c(0.1, 0.1, 0.1, 0.1), "lines"), 
                    label.color = NA) +
      geom_richtext(data = filter(., cat_pos == "Seronegative"), 
                    aes(x = pct,  y = mcat_symp, fill = cat_pos, 
                        label = pct, hjust = hjust, color = color), 
                    position = position_nudge(y = -0.2), 
                    size = 2.6, fill = "transparent",
                    label.padding = unit(c(0.1, 0.1, 0.1, 0.1), "lines"), 
                    label.color = NA) +
      geom_text(data = filter(., p_val < 0.05 & p_val >= 0.01 & cat_pos == "Seropositive"),
                aes(x = -0.7, y = mcat_symp), color = "black", fontface = "bold",
                label = "*", position = position_nudge(y = -0.05)) +
      geom_text(data = filter(., p_val < 0.01 & cat_pos == "Seropositive"),
                aes(x = -0.7, y = mcat_symp), color = "black", fontface = "bold",
                label = "**",  position = position_nudge(y = -0.05)) +
      scale_x_continuous(expand = expansion(add = c(1.6, 4))) +
      scale_fill_manual(values = c(seroneg_color, seropos_color)) +
      scale_color_manual(values = c("black", "white")) +
      theme(axis.text.y = element_text(face = "bold", color = "black"),
            axis.title.x = element_text(face = "plain"), 
            legend.position = c(0.75, 0.5), 
            legend.direction = "vertical", 
            plot.caption = element_text(face = "plain", color = "gray10")) +
      labs(x = "Percentage with each symptom", y = "", fill = "", 
           caption = paste("of", pos_cnt_for_caption, "seronegative and", 
                           neg_cnt_for_caption, "seropositive individuals"
                           )
           ) + 
      guides(fill = guide_legend(reverse = T), 
             color = F)
  }


```




## Have you taken one or several medications for symptoms characteristic of COVID-19?

(Denominator of percentages is those who reported at least one symptom compatible with COVID-19)

```{r fig.width=7, fig.height= 3.6}

yao_symptoms <- 
  yao %>% 
  filter(mcat_symp != "No symptoms")


yao %>%
  filter(mcat_symp != "No symptoms") %>%
  filter(mcat_drug != "No response") %>%
  filter(!is.na(mcat_drug)) %>% 
  plot_upset(cat_col = mcat_drug,
             intersect_cutoff = 2,
             denom = yao_symptoms,
             sep = "--"
             )

```



<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->
<!-- Divider divider you are here -->





## Seropositivity breakdown table 1

(see next page)

\newpage

```{r}

pos_count <- 
  yao %>% 
  filter(!is.na(cat_pos)) %>% 
  # summarise
  group_by(cat_pos) %>% 
  count(id_ind) %>% 
  count(n) %>% 
  ungroup() %>% 
  # transform
  select(pos = cat_pos,
         nn) %>% 
  mutate(Characteristic = "n") %>% 
  pivot_wider(id_cols = Characteristic, values_from = nn, names_from = pos) %>% 
  mutate(across(.fns = as.character))


mean_age <- 
  yao %>% 
  filter(!is.na(cat_pos)) %>% 
  # summarise
  group_by(cat_pos) %>% 
  summarise(mean_age = format(mean(val_age), digits = 3 ) , 
            sd = format(sd(val_age), digits = 3), 
            mean_sd = paste0(mean_age, " (", sd, ")")
            ) %>% 
  ungroup() %>% 
  # transform
  mutate(Characteristic = "Mean Age (SD)") %>% 
  pivot_wider(id_cols = Characteristic, values_from = mean_sd, names_from = cat_pos)


BMI_row <- 
  yao %>% 
  filter(!is.na(cat_pos)) %>% 
  # summarise
  group_by(cat_pos) %>% 
  summarise(mean_BMI = format(mean(val_BMI), digits = 3 ) , 
            sd = format(sd(val_BMI), digits = 3), 
            mean_sd = paste0(mean_BMI, " (", sd, ")")
            ) %>% 
  ungroup() %>% 
  # transform
  mutate(Characteristic = "Mean BMI (SD)") %>% 
  pivot_wider(id_cols = Characteristic, values_from = mean_sd, names_from = cat_pos)


tabulate_sero_categories <- function(df, col) {
  df %>%
    mutate(counter = 1) %>%
    group_by(cat_pos) %>%
    mutate(n_pos_neg = length(unique(id_ind))) %>%
    group_by(cat_pos, {{ col }}) %>%
    transmute(
      n_pos_neg_per_cat = sum(counter),
      n_pos_neg = n_pos_neg
    ) %>%
    slice(1) %>%
    ungroup() %>%
    mutate(
      pct = 100 * n_pos_neg_per_cat / n_pos_neg,
      pct = round(pct, 1)
    ) %>%
    # paste count and percentages
    mutate(n_pos_neg_per_cat = format(n_pos_neg_per_cat, digits = 5)) %>%
    mutate(nn_pct = paste0(n_pos_neg_per_cat, " (", pct, "%)")) %>%
    # transform
    select(
      Characteristic = {{ col }},
      pos = cat_pos,
      nn_pct
    ) %>%
    pivot_wider(id_cols = Characteristic, values_from = nn_pct, names_from = pos) %>%
    mutate(across(.fns = as.character))
}

sex_groups <- 
  yao %>% 
  filter(!is.na(cat_sex) & !is.na(cat_pos)) %>% 
  tabulate_sero_categories(cat_sex)

age_groups <- 
  yao %>% 
  mutate(cat_age = cut(val_age, 
                       breaks = c(4.9,15,29,45,65,100), 
                       labels = c("5-15", "16-29", "30-45", "46-65", "above 65")
                       )) %>%
  filter(!is.na(cat_age) & !is.na(cat_pos)) %>% 
  tabulate_sero_categories(cat_age)


education_levels <- 
  yao %>% 
  mutate(cat_educ = recode(cat_educ, "No response" = "Other")) %>% 
  mutate(cat_educ = fct_infreq(cat_educ), 
         cat_educ = fct_relevel(cat_educ, "Other", after = Inf)) %>% 
  filter(!is.na(cat_educ) & !is.na(cat_pos)) %>% 
  tabulate_sero_categories(cat_educ)


professions <- 
  yao %>% 
  # separate
  select(cat_pos, id_ind, mcat_occup) %>% 
  separate_rows(mcat_occup, sep = "--") %>% 
  mutate(mcat_occup = recode(mcat_occup, "No response" = "Other")) %>% 
  mutate(mcat_occup = fct_infreq(mcat_occup)) %>% 
  filter(!is.na(mcat_occup) & !is.na(cat_pos)) %>% 
  tabulate_sero_categories(mcat_occup)

symptoms <- 
  yao %>% 
  # separate
  select(cat_pos, id_ind, mcat_symp) %>% 
  separate_rows(mcat_symp, sep = "--") %>% 
  mutate(mcat_symp = fct_infreq(mcat_symp)) %>% 
  filter(!is.na(mcat_symp) & !is.na(cat_pos)) %>% 
  tabulate_sero_categories(mcat_symp)


sero_table <- 
  pos_count %>% 
  bind_rows(mean_age) %>% 
  bind_rows(BMI_row) %>% 
  add_row(Characteristic  = "Age groups, n (% of all positive/negatives that are of each sex)") %>% 
  bind_rows(sex_groups) %>% 
  add_row(Characteristic  = "Age groups, n (% of all positive/negatives that are in each age group)") %>% 
  bind_rows(age_groups) %>% 
  add_row(Characteristic  = "Education Level, n (% of all positive/negatives that are in each education class)") %>% 
  bind_rows(education_levels) %>% 
  add_row(Characteristic  = "Profession, n (% of all positive/negatives that are in each profession class)") %>% 
  bind_rows(professions) %>% 
  add_row(Characteristic  = "Symptoms, n (% of all positive/negatives that reported each symptom)") %>% 
  bind_rows(symptoms) %T>% 
  {which(is.na(.$Negative)) ->> rows_to_merge } %>% 
  huxtable() %>% 
  theme_basic() %>% 
  merge_across(row = rows_to_merge + 1) %>% 
  set_italic(row = c(rows_to_merge + 1), col = 1) %>% 
  set_latex_float("h!") %>% 
  set_all_padding(0.5)

sero_table
```


\newpage

## Symptoms reported (since March 1st)


All respondents. Denominator of percentages is everyone who was surveyed.

```{r fig.width = 7, fig.height = 4.1}

yao %>%
  plot_upset(mcat_symp,
             intersect_cutoff = 3,
             set_size_lab = "Prevalence \n(n and % with this symptom)",
             intersect_size_lab = "Co-prevalence \n (n and % with this combination of symptoms)")

```

Subset of those who have had symptoms. Denominator of percentages is everyone who was surveyed.

```{r fig.width = 7, fig.height = 4.1}

yao %>%
  filter(mcat_symp != "No symptoms") %>%
  plot_upset(mcat_symp,
             intersect_cutoff = 3,
             sep = "--",
             set_size_lab = "Prevalence \n(n and % with this symptom)",
             intersect_size_lab = "Co-prevalence \n (n and % with this combination of symptoms)"
             )

```

Subset of those who had a positive IgG or IgM test and have reported symptoms. Denominator of percentages is everyone who was seropositive.

```{r fig.width = 7, fig.height = 4.4}

seropos_sub <- yao %>%
  filter(cat_igg_result == "Positive" | cat_igm_result == "Positive") 

seropos_sub %>%
  filter(mcat_symp!= "No symptoms") %>% 
  plot_upset(mcat_symp,
             denom = seropos_sub,
             intersect_cutoff = 2,
             sep = "--",
              set_size_lab = "Prevalence \n(n and % with this symptom)",
             intersect_size_lab = "Co-prevalence \n (n and % with this combination of symptoms)"
             )

```

Subset of those who had negative test results for both the IgG and IgM and have reported symptoms. Denominator of percentages is everyone who was seronegative


```{r fig.width = 7, fig.height = 4.4}

seroneg_sub <- yao %>%
  filter(cat_igg_result == "Negative" & cat_igm_result == "Negative")

seroneg_sub %>%
  filter(mcat_symp!= "No symptoms") %>% 
  plot_upset(mcat_symp,
             denom = seroneg_sub,
             intersect_cutoff = 2,
             sep = "--",
             set_size_lab = "Prevalence \n(n and % with this symptom)",
             intersect_size_lab = "Co-prevalence \n (n and % with this combination of symptoms)"
             )
```



## Questions on respect of hygiene behavior


```{r fig.width=6, fig.height=6.5}
   
hygiene_survey_plot <- list( geom_col(position = "stack", width= 0.75) ,
  # geom_text(aes(label = countprop),
  #           position = "stack", vjust = -1, hjust = 1.5, color = "white",
  #           size = 3, fontface = "plain") ,
  geom_richtext(aes(label = countprop),
            position = "stack", vjust = 0.5, hjust = 1.1, size = 3.3, lineheight = 0.85, 
            label.size =0, color = "white", show.legend = FALSE, 
            label.padding = unit(c(0.1, 0.1, 0.1, 0.1), "lines")) ,
  coord_flip(clip = "off") ,
  scale_y_continuous(expand = expansion(add = c(0,0))) ,
  scale_fill_manual(limits = c("Definitely yes", "Partly", "Definitely not"), 
                    values = c( "#226EAE", "#7cb4f7", "#E75B30" )) ,
  theme_minimal() ,
  theme(plot.title = element_text(hjust = 0, face = "bold"),
        plot.title.position = "plot",
        axis.text.y = element_text(color = "black", size = 10, face = "bold"),
        legend.position = "top", 
        legend.direction = "horizontal", 
        legend.title = element_blank(), 
        panel.grid = element_blank(), 
        legend.text = element_text(size = 10), 
        axis.text.x = element_blank()) )

basic_hygiene <- 
yao %>%
  filter(!is.na(cat_pos) & !is.na(is_respecting_hygiene)) %>%
  filter(is_respecting_hygiene != "No response") %>%
  # filter(is_respecting_hygiene != "Partly" & is_respecting_hygiene != "No response") %>%
  group_by(cat_pos, is_respecting_hygiene) %>%
  summarise(n = n()) %>%
  group_by(cat_pos) %>%
  mutate(
    pct = 100 * n / sum(n),
    pct_paste = round(pct, 0),
    countprop = paste0(
     "<span style='color:white'><i><b>",
      pct_paste, "%", "</i></b></span>",
      "<br>", 
      "<span style='font-size:7pt'>",
      "n = ",
      n,
      "  </span>"
    ), 
    countprop = if_else(pct >= 7, countprop, NA_character_)
  ) %>%
  mutate(cat_pos = factor(cat_pos,
    levels = c("Positive", "Negative")
  )) %>%
  mutate(cat_pos = recode(cat_pos, "Positive" = "Seropositive", "Negative" = "Seronegative")) %>%
  mutate(is_respecting_hygiene = factor(is_respecting_hygiene,
    levels = c("Definitely not", "Partly", "Definitely yes")
  )) %>%
  ggplot(aes(x = cat_pos, y = pct, fill = is_respecting_hygiene)) +
  labs(
    title = str_wrap("Do you follow the basic hygiene protocols (wash hands frequently, 
                        sneeze in your elbow, use a disposable tissue, etc.)", 64),
    x = "", y = ""
  ) +
  hygiene_survey_plot



social_distancing <- 
yao %>%
  filter(!is.na(cat_pos) & !is.na(is_respecting_distancing)) %>%
  filter(is_respecting_distancing != "No response") %>%
  # filter(is_respecting_hygiene != "Partly" & is_respecting_hygiene != "No response") %>%
  group_by(cat_pos, is_respecting_distancing) %>%
  summarise(n = n()) %>%
  group_by(cat_pos) %>%
 mutate(
    pct = 100 * n / sum(n),
    pct_paste = round(pct, 0),
    countprop = paste0(
     "<span style='color:white'><i><b>",
      pct_paste, "%", "</i></b></span>",
      "<br>", 
      "<span style='font-size:7pt'>",
      "n = ",
      n,
      "  </span>"
    ), 
      countprop = if_else(pct >= 7, countprop, NA_character_)
  ) %>%
  mutate(cat_pos = factor(cat_pos,
    levels = c("Positive", "Negative")
  )) %>%
  mutate(cat_pos = recode(cat_pos, "Positive" = "Seropositive", "Negative" = "Seronegative")) %>%
  mutate(is_respecting_distancing = factor(is_respecting_distancing,
    levels = c("Definitely not", "Partly", "Definitely yes")
  )) %>%
  ggplot(aes(x = cat_pos, y = pct, fill = is_respecting_distancing)) +
  labs(
    title = str_wrap("Do you follow social distancing rules (avoid handshakes or hugs, 
                        avoid unnecessary outings, etc.)", 64),
    x = "", y = ""
  ) +
  hygiene_survey_plot +
  theme(legend.position = "none")


confinement <- 
yao %>%
  filter(!is.na(cat_pos) & !is.na(is_staying_confined)) %>%
  filter(is_staying_confined != "No response") %>%
  # filter(is_respecting_hygiene != "Partly" & is_respecting_hygiene != "No response") %>%
  group_by(cat_pos, is_staying_confined) %>%
  summarise(n = n()) %>%
  group_by(cat_pos) %>%
  mutate(
    pct = 100 * n / sum(n),
    pct_paste = round(pct, 0),
    countprop = paste0(
     "<span style='color:white'><i><b>",
      pct_paste, "%", "</i></b></span>",
      "<br>", 
      "<span style='font-size:7pt'>",
      "n = ",
      n,
      "  </span>"
    ), 
    countprop = if_else(pct >= 7, countprop, NA_character_)
  ) %>%
  mutate(cat_pos = factor(cat_pos,
    levels = c("Positive", "Negative")
  )) %>%
  mutate(cat_pos = recode(cat_pos, "Positive" = "Seropositive", "Negative" = "Seronegative")) %>%
  mutate(is_staying_confined = factor(is_staying_confined,
    levels = c("Definitely not", "Partly", "Definitely yes")
  )) %T>%
  {
    . ->> data_to_plot
  } %>%
  ggplot(aes(x = cat_pos, y = pct, fill = is_staying_confined)) +
  labs(
    title = str_wrap("Since March 1st, have you stayed confined?", 64),
    x = "", y = ""
  ) +
  hygiene_survey_plot +
  theme(legend.position = "none")


line_sep <- 
  linesGrob(unit(c(0, 1), "npc"), unit(1, "npc"),
                            gp = gpar(col = 'lightgrey', lwd = 4)) %>% 
  wrap_elements()

patchwork::wrap_plots(basic_hygiene, line_sep, social_distancing, line_sep, confinement, 
                      ncol = 1, heights = c(1,0.1,1,0.1,1))


```

































